Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-02-16 analysis/paper/paper.Rmd

---
title: "Assessment of the KLGO Coastal Waterbird Survey Monitoring Program"
author:
- name: Joel H. Reynolds^[U.S. National Park Service, Alaska Region, Natural Resources
    Science Team]
- name: Madeleine Ward^[Swarthmore College, Dept. of Mathematics and Statistics]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::word_document2:
    fig_caption: yes
    toc: yes
  html_document:
    df_print: paged
    fig_caption: yes
    number_sections: yes
    toc: yes
  pdf_document:
    fig_caption: yes
    toc: yes
keywords: keyword 1; keyword 2; keyword 3
link-citations: yes
bibliography: KLGOCWS_References.bib
abstract: The Coastal Waterbird Survey has been conducted, with varying levels of
  effort and in-season frequency, since 2003 [@Surdyk2018]. The area of interest has
  been divided into eight contiguous survey units; on each survey, at each unit the
  number, age, composition (sex), breeding status, and noteworthy behavioral observations
  are recorded for each species [@Anonymous2009]. Given the constraints on personnel,
  time, and budgets, it is imperative that surveys be conducted efficiently in terms
  of both choice of sampling design and choice of sampling effort. Now that KLGO has
  multiple years of experience implementing the protocol, it is timely to step back
  and assess how things are going. We review the current program's objectives and
  survey design, identify statistical issues, and recommend potential solutions. Major
  topics include... blah blah. The study concludes with a series of recommended tasks
  that the park should undertake to improve the coastal waterbird survey's efficiency
  and effectiveness.
---

>>>>

---
title: "Assessment of the KLGO Coastal Waterbird Survey Monitoring Program"
author:
- name: Joel H. Reynolds^[U.S. National Park Service, Alaska Region, Natural Resources
    Science Team]
- name: Madeleine Ward^[Swarthmore College, Dept. of Mathematics and Statistics]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::word_document2:
    fig_caption: yes
    toc: yes
  html_document:
    df_print: paged
    fig_caption: yes
    number_sections: yes
    toc: yes
  word_document:
    toc: yes
    fig_caption: true
    reference_docx: NRR_Author_Template_V4.2.docx
  pdf_document:
    fig_caption: yes
    toc: yes
    fig_caption: true
keywords: keyword 1; keyword 2; keyword 3
link-citations: yes
bibliography: KLGOCWS_References.bib
abstract: The Coastal Waterbird Survey has been conducted, with varying levels of
  effort and in-season frequency, since 2003 [@Surdyk2018]. The area of interest has
  been divided into eight contiguous survey units; on each survey, at each unit the
  number, age, composition (sex), breeding status, and noteworthy behavioral observations
  are recorded for each species [@Anonymous2009]. Given the constraints on personnel,
  time, and budgets, it is imperative that surveys be conducted efficiently in terms
  of both choice of sampling design and choice of sampling effort. Now that KLGO has
  multiple years of experience implementing the protocol, it is timely to step back
  and assess how things are going. We review the current program's objectives and
  survey design, identify statistical issues, and recommend potential solutions. Major
  topics include... blah blah. The study concludes with a series of recommended tasks
  that the park should undertake to improve the coastal waterbird survey's efficiency
  and effectiveness.
---
